\chapter*{Acknowledgement}
\markboth{Acknowledgement}{Acknowledgement}


\singlespace{I owe such an intellectual debt to so many individuals that it feels like the true author list for this dissertation should be half its content.
Most prominently I would like to thank my primary advisor Frank Doyle for his unwavering support during this process. 
It's only in retrospect that I can understand how valuable your contributions were to the development of my thinking.
To my coadvisors, Professors Linda Petzold and Beth Klerman, and my additional mentors Professors Erik Herzog and Hyunmin Yi: thank you for committing your time and intellectual energy to my development.
Sorry for the late hours at which I replied to your emails.
I've also been quite lucky to have a remarkable cast of collaborators, and I would like to thank Vania Carmona-Alcocer, Ankush Chakrabarty, Brian Drawert, Daniel Granados-Fuentes, Cristina Mazuski, Peter St.\ John, and Steffen Waldherr.
I'm humbled to be considered your peer.
In particular, Peter St.\ John's mentorship has had a disproportionate positive effect on my research, and for that I am grateful.
I am also grateful for the community that the entire Doyle group has been throughout my time in it.
From squash, to ill-advised witch hunts (apologies to Lindsey Brown, no apologies to Kelsey Dean), to Thanksgivings at Eyal's, it's been a remarkable time.
Thank you especially to Alejandro Laguna, Kelsey Dean, Faith Barcelo, Eyal Dassau, Sunil Deshpande, Joon Bok Lee, Ravi Gondhalekar, and Gunjan Thakur for moving across the country with me.


I have been extraordinarily privileged to have had the support of numerous educators and institutions, all of which contributed to my completion of this dissertation.
Harvard, UC Santa Barbara, and Tufts have been fantastic developmental environments to which I hope to return frequently.
To Liz Pomerantz and Sam Reed: I could not have survived here without your help, and the Systems Biology program has felt like an intellectual home ever since I arrived on campus.
Finally, I would like to thank the educators who inspired me to embrace challenging questions from early on, especially Matthew McDonough, Thomas Morey, and Sr.\ Carol Ann Murray.

To my family
\{Anthony, Frederick, Joseph, Judy, Katrina, Virginia\} Abel, \{Faith, Kim\} Blake, \{Alyssa, Mary\} Miller:
thank you for making me who I am. I hope I have made you proud.
I would like to especially acknowledge Faith Blake for her often unnoted intellectual contributions to my work, most prominently in interpreting data recorded from the fetal suprachiasmatic nucleus and in editing and questioning every manuscript I have written.
It seemed out of place to acknowledge you on the papers, in that all of my ideas were also fundamentally yours.
I hope that I can contribute to your career even half of what you have to mine.
I would also like to thank my friends, but in lieu of listing names I'll list locations significant to us: Beacon Hill, Big Sur, Hemenway, Holualoa, Indio, Isla Vista, the Louvre, West End Avenue, Winthrop.
}

